Bioverse: Origins of Life

### 2024-06-19 src/tex/ms.tex
update conclusions

Our main findings are:
\begin{enumerate}
    \item Models of the Origins of Life provide hypotheses that are testable with near-future exoplanet surveys.
    \item The required \gls{NUV} radiation in the cyanosulfidic scenario should lead to a correlation between past \gls{NUV} flux and current occurrence of biosignatures, both of which will soon be observationally accessible.
    \item The required sample size for detecting this correlation depends on the occurrence of life on temperate exoplanets, the distribution of host star spectral types in the sample, ...
%        A direct imaging mission with the \gls{HWO} will require characterizing XXX planets ...
    \item If the predicted \gls{NUV} correlation exists, yielding strong evidence for it is likely ($> \SI{90}{\percent}$) for sample sizes $\geq 100$, and a survey strategy that targets extreme values of inferred past \gls{NUV} irradiation.
    \item Abiogenesis in the cyanosulfidic scenario strongly prefers late host star spectral types in a sample of transiting planets. Any potential biosignature detection on a planet around a star other than an M~dwarf would disvafor this scenario and any other \gls{ool} theory requiring extended periods of high \gls{NUV} irradiation.
\end{enumerate}

>>>>

Our main findings are:
\begin{enumerate}
    \item Models of the Origins of Life provide hypotheses that are testable with near-future exoplanet surveys.
    \item The required \gls{NUV} radiation in the cyanosulfidic scenario should lead to a correlation between past \gls{NUV} flux and current occurrence of biosignatures, both of which will soon be observationally accessible.
    \item The required sample size for detecting this correlation depends on the occurrence of life on temperate exoplanets and the distribution of host star spectral types in the sample; in particular their past maximum \gls{NUV} fluxes.
%        A direct imaging mission with the \gls{HWO} will require characterizing XXX planets ...
    \item If the predicted \gls{NUV} correlation exists, yielding strong evidence for it is likely ($> \SI{90}{\percent}$) for sample sizes $\geq 100$, and a survey strategy that targets extreme values of inferred past \gls{NUV} irradiation.
    \item Abiogenesis in the cyanosulfidic scenario prefers late host star spectral types due to the higher \gls{NUV} fluxes in their habitable zones. However, despite the overall lower biosignature rate, the distribution of maximum past \gls{NUV} fluxes in a transit survey targeting planets around FGK stars is beneficial for Bayesian hypothesis testing.
%     in a sample of transiting planets. Any potential biosignature detection on a planet around a star other than an M~dwarf would disvafor this scenario and any other \gls{ool} theory requiring extended periods of high \gls{NUV} irradiation.
\end{enumerate}
